\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-14 paper_resources/doc/paper.tex
Minor polishing

\section{Additional statistical analysis}\label{sec:appendix-2}

\begin{figure}[H]
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
		\caption{No noise}
		\label{fig:CDplotsR2-no-noise}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.4\textwidth}

		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
		\caption{Level of noise equal to 0.001}
		\label{fig:CDplotsR2-noise0.001}
	\end{subfigure}
	\centering
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
		\caption{Level of noise equal to 0.01.}
		\label{fig:CDplotsR2-noise0.01}
	\end{subfigure}
	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
	\label{fig:cd-plotsR2-varying_noise}
\end{figure}

>>>>

%\section{Additional statistical analysis}\label{sec:appendix-2}

%\begin{figure}[H]
%	\begin{subfigure}[b]{0.40\textwidth}
%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
%		\caption{No noise}
%		\label{fig:CDplotsR2-no-noise}
%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[b]{0.4\textwidth}
%		
%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
%		\caption{Level of noise equal to 0.001}
%		\label{fig:CDplotsR2-noise0.001}
%	\end{subfigure}
%	\centering
%	\begin{subfigure}[b]{0.40\textwidth}
%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
%		\caption{Level of noise equal to 0.01.}
%		\label{fig:CDplotsR2-noise0.01}
%	\end{subfigure}
%	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
%	\label{fig:cd-plotsR2-varying_noise}
%\end{figure}
